Road Segment Prioritization for Bicycle Infrastructure

### 2021-03-06 README.Rmd
Complete edits

The approach is also focused solely on the allocation of cycling
infrastructure, and does not consider the larger political and
regulatory environment that needs to exist to promote cycling; while
segregated, connected, and direct cycling infrastructure is key to
achieving high levels of cycling, research has shown that it cannot
exist in a vacuum. @wardman2007factors developed a mode choice model
for the UK and their results showed that improved cycling infrastructure
on its own only had modest impacts on mode shift, and even the unlikely
scenario of all urban routes being serviced by segregated bike lanes was
forecast to increase cycling mode share by only 3%. International
research shows that cities that invest in more comprehensive cycling
projects have a more significant increase in the number of cyclists as
well as the cycling mode share [@parkin2018designing;
@pucher2010infrastructure]. These cities do not just focus on
infrastructure, but on general policies as well as restricting car use.
Evaluation of policies in Denmark and Germany and the Netherlands has
shown that their high cycling mode share is down to a broader set of
soft and hard policies. Hard policies include traffic calming, filtered permeability
interventions, cycling rights of way, bike parking, integration with the
public transport network, and making driving cars both expensive and
inconvenient, while soft policies include marketing and awareness compaigns [@gossling2013urban; @pucher2008making]. While these policies are outside the scope of this research, it is important to recognize their key role in
bringing about an increase in levels of cycling.

The methods can support the ongoing shift towards active transport,
which is one of the priority areas of investments worldwide in transport
planning. This necessary shift predates the pandemic and is driven by
ambitions to improve the health and well-being of the citizens
worldwide. The success of such a shift depends on the appeal of the
cycling network for prospective cyclists, together with policies and
interventions deterring the usage of the private car.

>>>>

The approach is also focused solely on the allocation of cycling
infrastructure, and does not consider the larger political and
regulatory environment that needs to exist to promote cycling; while
segregated, connected, and direct cycling infrastructure is key to
achieving high levels of cycling, research has shown that it cannot
exist in a vacuum. @wardman2007factors developed a mode choice model
for the UK and their results showed that improved cycling infrastructure
on its own only had modest impacts on mode shift, and even the unlikely
scenario of all urban routes being serviced by segregated bike lanes was
forecast to increase cycling mode share by only 3%. International
research shows that cities that invest in more comprehensive cycling
projects have a more significant increase in the number of cyclists as
well as the cycling mode share [@parkin2018designing;
@pucher2010infrastructure]. These cities do not just focus on
infrastructure, but on general policies as well as restricting car use.
Evaluation of policies in Denmark and Germany and the Netherlands has
shown that their high cycling mode share is down to a broader set of
soft and hard policies. Hard policies include traffic calming, filtered permeability
interventions, cycling rights of way, bike parking, integration with the
public transport network, and making driving cars both expensive and
inconvenient, while soft policies include marketing and awareness campaigns [@gossling2013urban; @pucher2008making]. While these policies are outside the scope of this research, it is important to recognize their key role in
bringing about an increase in levels of cycling.

Consideration of these limitations suggest future directions of research.
New datasets and continuously evolving computational (hardware and software)
capabilities should enable the data related issues to be overcome as open
datasets, and our ability to process them, improve.
Plugging-in alternative uptake models could help address the relatively narrow
definition of 'potential' used in this paper, to consider broader social factors.
A promising area of future research in this direction could be 
to integrate a wider range of modes, including e-bikes and e-scooters, into the
analysis. Currently scope for progress in this direction is
partially restricted by the lack of data on the
proliferation of these modes, raising the point that surveys could
replace the broad category of `Bicycle' a range of small modes such as
'pedal cycles' (including tricycles and recumbent cycles), e-bikes
and other forms of micro-mobility.

Despite the rapid growth of these alternative modes, there is little doubt that
the humble bicycle is a key ingredient in the ongoing shift towards active transport.
Recognition of the importance of this shift for improved the health and well-being
the citizens, and the wider challenge to decarbonise the global economy,
has grown with pressures on health and public transport systems during the pandemic.
The success of policies to accelerate cycling uptake depends on a range of
factors including, vitally, the design of the
cycling network for potential cyclists.
The approach presented in this paper provides a strong evidence base,
that considers both cycling potential and social equity,
for designing joined-up and cost-effective strategic cycle networks.
<!-- In tandem with policies to reduce excessive reliance on private cars, evidence-based investment in strategic cycle networks is key to. -->
